Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Move todo item to GH issues
Misc cleanup

\todo[inline]{Add a thicker dashed line at $y= -0.5m$, and maybe a dashed 1m
circle in the top view of the turbine.}

@@

Mean power and drag coefficients at $\lambda=1.9$ are plotted vs.\ Reynolds
number in Figure~\ref{fig:perf-Re-dep}. There is a drastic improvement in $C_P$
with increasing Reynolds number at lower values of Reynolds number. The power
coefficient then becomes  essentially $Re$-independent at $Re_D = 0.8 \times
10^6$, which corresponds to an approximate average blade chord Reynolds number
$Re_{c, \mathrm{ave}} = 2.1 \times 10^5$. This threshold is consistent with the
behavior of the blade boundary layer transitioning from laminar to turbulent,
thereby promoting reattachment of the laminar separation bubble.
\todo[inline]{Is there still a laminar separation bubble near the leading edge
    at these Reynolds numbers?}

>>>>

@@

Mean power and drag coefficients at $\lambda=1.9$ are plotted versus Reynolds
number in Figure~\ref{fig:perf-Re-dep}. There is a drastic improvement in $C_P$
with increasing Reynolds number at lower values of Reynolds number. The power
coefficient then becomes  essentially $Re$-independent at $Re_D = 0.8 \times
10^6$, which corresponds to an approximate average blade chord Reynolds number
$Re_{c, \mathrm{ave}} = 2.1 \times 10^5$. This threshold is consistent with the
behavior of the blade boundary layer transitioning from laminar to turbulent,
thereby promoting reattachment of the laminar separation bubble.

\todo[inline]{Is there still a laminar separation bubble near the leading edge
    at these Reynolds numbers?}
